\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
Fix a typo and then replace XXX with 300 for now.  This summary looks pretty good to me, thanks Jeroen and Dirk for greatly improving it.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@819 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Summary}  % DE Simpler title
\label{sec:summary}
% TODO(mstokely): Get cibona approval for these two sentences before
% publishing
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as CSV and JSON are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
The Protocol Buffers protocol and librart offers a unique combination of features, performance,
maturity, and forward-compatibility that seems particulary well suited for data-driven 
applications and numerical computing.

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than XXX 30-day active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.

>>>>

\section{Summary}  % DE Simpler title
\label{sec:summary}
% TODO(mstokely): Get cibona approval for these two sentences before
% publishing
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as CSV and JSON are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
The Protocol Buffers protocol and library offers a unique combination of features, performance,
maturity, and forward-compatibility that seems particulary well suited for data-driven 
applications and numerical computing.

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than 300 30-day active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.
